% Credit for template: https://github.com/arasgungore/arasgungore-CV

\documentclass[letterpaper,10pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%---------- HEADING ----------

\begin{center}
  \textbf{\Huge Tushar Chenan} \\ \vspace{3pt}
  \small
  \faEnvelope \hspace{.5pt} \href{mailto:tusky2002@gmail.com}{tusky2002@gmail.com}
  $|$
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/tushar-chenan/}{LinkedIn}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/rocka0}{GitHub}
  $|$
  \faCc \hspace{.5pt} \href{https://www.codechef.com/users/getmeto5stars}{CodeChef}
  $|$
  \faCode \hspace{.5pt} \href{https://codeforces.com/profile/14122021}{CodeForces}
\end{center}

%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
\resumeSubHeadingListStart

\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{Birla Institute of Technology \& Science, Pilani} & Hyderabad, India \\
  \textit{\small B.E. in Computer Science and Engineering; \textbf{CGPA: 9.69/10.00}} & \textit{\small Nov 2020 \textbf{--} July 2024} \\
\end{tabular*}\vspace{-5pt}
\resumeItemListStart
\resumeItem{\textbf{Major coursework:} Operating Systems, Data Structures and Algorithms, Computer Architecture, Computer Networks, Compiler Construction, Software Engineering, Database Systems, Object-Oriented Programming}
\resumeItem{\textbf{Additional coursework:} Foundations of Data Science, Design and Analysis of Algorithms, Computational Geometry, Theory of Computation, Discrete Structures for Computer Science, Professional Ethics, Game Theory}
\resumeItemListEnd

\vspace{-2pt}\item
\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
  \textbf{National Public School} & Bangalore, India \\
  \textit{\small CBSE Class XII; \textbf{CGPA: 9.64/10.00}} & \textit{\small July 2020} \\
  \textit{\small CBSE Class X; \textbf{CGPA: 9.56/10.00}} & \textit{\small July 2018} \\
\end{tabular*}\vspace{-7pt}

\resumeSubHeadingListEnd

%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
              \textbf{Languages:}{ C, C++, Python, JavaScript, HTML/CSS, SQL} \\ \vspace{3pt}
              \textbf{Technologies and Frameworks:}{ MySQL, MongoDB, Express.js, React.js, Git, Docker, GraphQL} \\ \vspace{3pt}
        }}
\resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Work Experience}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeSubheading
{Google}{Bangalore, India}
{Software Engineering Intern}{Jun 2023 \textbf{--} Aug 2023}
\resumeItemListStart
\resumeItem{Google developed an auxiliary cache on top of the MySQL InnoDB storage engine’s buffer pool for improved database performance.}
\resumeItem{Designed a verification utility to ensure data integrity and metadata consistency of this secondary cache.}
\resumeItem{The utility was written in C++. Automated unit/end-to-end tests were written with MTR (MySQL Test Run).}
\resumeItem{Gained a deep understanding of the InnoDB storage engine, buffer pool and the MySQL database architecture.}
\resumeItemListEnd

\resumeSubheading
{Centre for Development of Advanced Computing (C-DAC)}{Pune, India}
{Full-Stack Development Intern}{Jun 2022 \textbf{--} Jul 2022}
\resumeItemListStart
\resumeItem{Developed a digital marketing website for super-computing systems and AI/ML APIs built by C-DAC.}
\resumeItem{Front-end was built with React.js and is styled with Bootstrap CSS. Back-end was built with Python-Django and exposes a REST API.}
\resumeItem{Features a chatbot built with Google’s Dialog-Flow for an enhanced user experience.}
\resumeItem{Incorporated continuous integration and deployment of the code repository to Heroku.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- PROJECTS -----------

\section{Projects}
\vspace{3pt}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{Shiftrr.} $|$ MERN Stack Application}{Jan 2022 \textbf{--} May 2022}
\resumeItemListStart
\resumeItem{A platform for students to hire and offer freelance services in fields such as Web and App Development, Graphics Design, Music Production, and so on.}
\resumeItem{Front-end was built with Next.js. Back-end was built with Node.js (Express) and MongoDB (Mongoose).}
\resumeItem{Features automated unit tests, code coverage with Jest, Mocha and Chai, and deployment with GitHub Actions to Vercel.}
\resumeItem{Developed while following Scrum guidelines and general Agile principles.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{CRUx Forum} $|$ MERN Stack Application}{Jun 2021 \textbf{--} May 2022}
\resumeItemListStart
\resumeItem{A platform for campus-wide communication which enables clubs and departments to share notices with students while allowing students to comment and tag users.}
\resumeItem{Front-end was built with React.js, using Tailwind CSS for styling. Back-end was built with Node.js, MongoDB and Apollo GraphQL.}
\resumeItem{Unit testing and code coverage handled by Jest, Mocha and Chai. Deployed via GitHub actions to AWS.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
\vspace{2pt}
\resumeSubHeadingListStart
\small{\item{
              \textbf{Merit Scholarship:}{ Awarded a 100\% Merit Scholarship for being in the top 1\% academically in my batch.} \\ \vspace{3pt}
              \textbf{Indian Olympiad in Informatics (INOI):}{ Top 158 among 835 students who qualified for the Indian Olympiad in Informatics.} \\ \vspace{3pt}
              \textbf{HP Codewars, Bangalore:}{ Rank 1 out of 100+ schools at HP Codewars, Bangalore 2019.} \\ \vspace{3pt}
              \textbf{ICPC Regionalist:}{ Rank 117/1107 at the 2020 ICPC Asia Gwalior-Pune Regional Contest.} \\ \vspace{3pt}
              \textbf{Meta Hacker Cup:}{ Global rank 833 in Meta Hacker Cup 2023 Round 2.} \\ \vspace{3pt}
              \textbf{Expert on CodeForces:}{ Peak rating of 1601 (Expert) on CodeForces.} \\ \vspace{3pt}
              \textbf{5 stars on CodeChef:}{ Peak rating of 2054 (5 stars) on Codechef.} \\ \vspace{3pt}
        }}
\resumeSubHeadingListEnd

\end{document}
